The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-08-23 script/en/chapters/what-is-sage.tex
Corrected typos and overfull hbox; congruent index (no redundancy in wording; adjectives in lowercase in German; all normal words in lowercase in English)
CT Book ed 12: Major update -- many changes, corrections, and additions during last 4 months

% ---------------------------------------------------------------------------
\newpage
\hypertarget{appendix-using-sage}{}
\section{Short Introduction into the Computer Algebra System SageMath}
\label{s:appendix-using-sage}
\index{SageMath}
\index{SageMath!Code examples}

@@

   % Leerzeile am Ende nötig, sonst hat die zweite Zeile KEINEN hängenden Einzug?! (TODO)
   % Dadurch aber mehr Abstand von Seitennummer als sonst!
}.

@@

% ---------------------------------------------------------------------------
\newpage
\section*{Some examples using the built-in mathematical functions in SageMath}

@@

\noindent\hangindent=6pt\makebox[6pt][l]{-}If you run your script as above,
then SageMath first parses your script,
writes it to another file called ``primroots.py'' (note the ``.py''
extension), adds all necessary variables to "primroots.py" as well as
writing any import statements to that file. That way, your SageMath script
is executed as if you had typed the definitions in your script to the
SageMath command line. An important difference isthat all output needs a
\verb!print! statement.

>>>>

% $Id: 
% ..............................................................................
%             W H A T  I S  S A G E M A T H  ?
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\newpage
\hypertarget{appendix-using-sage}{}
\section{Short Introduction into the CAS SageMath}
\label{s:appendix-using-sage}
\index{SageMath}
\index{SageMath!code examples}

@@

   % Leerzeile am Ende nötig, sonst hat die zweite Zeile KEINEN hängenden Einzug?! (TODO_LaTeX)
   % Dadurch aber mehr Abstand von Seitennummer als sonst!
}.

@@

% ---------------------------------------------------------------------------
\newpage
\section*{Examples using the built-in mathematical functions in SageMath}

@@

\noindent\hangindent=6pt\makebox[6pt][l]{-}If you run your script as above,
then SageMath first parses your script, writes it to another file called
``primroots.py'' (note the ``.py'' extension), adds all necessary variables
to ``primroots.py'' as well as writing any import statements to that file.
That way, your SageMath script is executed as if you had typed the definitions
in your script to the SageMath command line. An important difference is that
all output needs a \verb!print! statement.
